Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-05 article.tex
Explain low-pass, high-pass, hard-tresholding, power filter

% Introduce filtering
\section{Signal filtering methodology}

The filtering process is made of three main parts:

\begin{enumerate}[i.]
\item A low-pass filter: we consider four shapes of local averaging,
\item A high pass filter : we apply the asymmetric discrete derivative,
\item A non-linear filter: we re-weight samples depending on the current
      activity of the systems in order to favour the association measure when
      directly connected neurons are firing together, while artificially
      reducing the association measure in case of extreme network activity,
      i.e. high when a network firing is happening and low when no neuron is
      active.
\end{enumerate}

>>>>

\section{Signal filtering methodology}

% Explain why we need to filter
% TODO

% Filtering methodology
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters. A low-pass filter, a high-pass
filter and a non linear hard-thresholding based filter are
applied for each possible time step $t$
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 a_l X_{t+l,i} \forall i, \\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
\end{align}
where the $a_l$ coefficients were taken in one of the four following tuples
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is the minimal
fluorescence signal .

%     4/ non-linear filter based on the neuron activations

\begin{enumerate}[i.]
\item A non-linear filter: we re-weight samples depending on the current
      activity of the systems in order to favour the association measure when
      directly connected neurons are firing together, while artificially
      reducing the association measure in case of extreme network activity,
      i.e. high when a network firing is happening and low when no neuron is
      active.
\end{enumerate}
